Dynein walks like an Imperial AT-ST

### 2018-08-20 papers/paper/paper.tex
Use gridspec to better format some figures
minor changes

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cm \Delta G_{ATP}$ &  & \\
$c_m$ & $\cb \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & & \\
$L_s$ & $\ls nm$ & 21nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$L_t$ & $\lt nm$ & 23nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{burgess-paper}\\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{burgess-paper}\\
$\theta_t$ & $\eqt$ &  & \\
$R_t$ & $\radiust$ & 8nm & \cite{burgess-paper}\\
$R_m$ & $\radiusm$ & 11nm & \cite{burgess-paper}\\
$R_b$ & $\radiusb$ & 3.5nm & \cite{burgess-paper}\\

@@

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_stepping_length_histogram}
  \includegraphics[width=\linewidth]{../../plots/paper_dwell_time_histogram}
  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
\caption{\textbf{Basic behavior of our model}}
\label{fig:}
\end{figure}

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_onebound_histogram.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}

>>>>

\begin{table}[tbhp]
\centering
\caption{Parameters used in model simulation.}
\label{tab:staticparams}
\begin{tabular}{lrrr}
Parameter & Model & Experimental & Source \\
\midrule
$c_b$ & $\cb \Delta G_{ATP}$ &  & \\
$c_m$ & $\cm \Delta G_{ATP}$ &  & \\
$c_t$ & $\ct \Delta G_{ATP}$ &  & \\
$k_b$ & $\kb s^{-1}$&  & \\
$k_{ub}$ & $\kub s^{-1}$ & & \\
$L_s$ & $\ls nm$ & 21nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$L_t$ & $\lt nm$ & 23nm & \cite{burgess-paper, 3vkh-cite, carter-paper}\\
$c$ & $\cexp$ & & \\
$\theta_b$ & $\eqb$ &  120 & \cite{leschziner} \\
$\theta_m^{\mbox{pre}}$ & $\eqmpre$ &  197 & \cite{burgess-paper}\\
$\theta_m^{\mbox{post}}$ & $\eqmpost$ & 242 & \cite{burgess-paper}\\
$\theta_t$ & $\eqt$ &  & \\
$R_t$ & $\radiust$ & 8nm & \cite{burgess-paper}\\
$R_m$ & $\radiusm$ & 11nm & \cite{burgess-paper}\\
$R_b$ & $\radiusb$ & 3.5nm & \cite{burgess-paper}\\

@@

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_model_behavior}
  \includegraphics[width=\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
\caption{\textbf{Basic behavior of our model}}
\label{fig:}
\end{figure}

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
  \includegraphics[width=\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}
